Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-04-25 Grassmannian_cells.tex
Proof of Lemma 4.2

We will always choose the subset $\{1,\ldots,k\}$ when using Lemma~\ref{le:preprojective lifts}.2 and thus we denote the cokernel simply by $\tilde P_m^{(k)}$.

\begin{lemma}
  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1,i})$ has a cell decomposition, then $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P_{m-1,i_j})$ has a cell decomposition.
\end{lemma}
\begin{proof}
This follows by induction and by considering the Caldero-Chapoton map. Then we can use the fact that every subrepresentation $U$ of $\tilde P_{m-1}$ is preprojective whence every proper factor is preinjective $V$ which means that we have $\Ext(U,V)=0$.  
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
\begin{thebibliography}{10}
\bibitem{ass}
Assem, I., Simson, D., Skowronski, A.: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
\bibitem{bgp}
Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
\bibitem{gab} Gabriel, P.: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
\bibitem{hr} Happel, D., Ringel, C.M.: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
\bibitem{rin} Ringel, C.M.: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).

>>>>

\end{proof}
If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$. The short exact sequence $\ses{\tilde P_{m-1,k}}{\tilde P_{m}^{(k-1)}}{\tilde P_{m}^{(k)}}$ induces a map between quiver Grassmannians
$$\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff( \tilde P_{m-1,k})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}),\,U\mapsto (U\cap \tilde P_{m-1,k},\pi(U))$$
which is sometimes called Caldero-Chapoton map.

\begin{lemma}
  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ has a cell decomposition into affine spaces, then $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j\geq 1$.
\end{lemma}
\begin{proof}The claim follows by induction whence considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}).$$

Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$. But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$. Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$. In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side. Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$. By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this bundle down) and thus itself trivial as a vector bundle over an affine space.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
\begin{thebibliography}{10}
\bibitem{ass}
Assem, I., Simson, D., Skowronski, A.: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
\bibitem{bgp}
Bernstein, I.~N., Gelfand, I.~M., Ponomarev, V.~A.: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
\bibitem{cc}
Caldero, P., Chapoton, F.: Cluster algebras as {H}all algebras of quiver representations.
Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).

\bibitem{gab} Gabriel, P.: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
\bibitem{hr} Happel, D., Ringel, C.M.: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}, no.2, 399-443 (1982).
\bibitem{rin} Ringel, C.M.: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}, no. 3, 465-479 (1980).
